\documentclass{article}[a4paper]
\usepackage[a4paper, left=2.5cm,right=2cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{mathtools}% http://ctan.org/pkg/mathtools
\usepackage{caption}
\captionsetup{width=.75\textwidth}
\usepackage[usestackEOL]{stackengine}
\usepackage{float}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric,arrows,positioning,fit}
\usetikzlibrary{shapes,calc,arrows}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{subfiles}
\usepackage{blindtext}
\usepackage{hyperref}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{xparse}
\usepackage{pmboxdraw}
\usepackage[utf8]{inputenc}
\NewDocumentCommand{\codeword}{v}{%
\texttt{\textcolor{blue}{#1}}%
}
\lstdefinestyle{tree}{
literate=
{├}{{\smash{\raisebox{-1ex}{\rule{1pt}{\baselineskip}}}\raisebox{0.5ex}{\rule{1ex}{1pt}}}}1 
{─}{{\raisebox{0.5ex}{\rule{1.5ex}{1pt}}}}1 
{└}{{\smash{\raisebox{0.5ex}{\rule{1pt}{\dimexpr\baselineskip-1.5ex}}}\raisebox{0.5ex}{\rule{1ex}{1pt}}}}1 
}

\def\XXX#1{\textcolor{red}{XXX #1}}
\newcommand{\vect}[1]{\boldsymbol{#1}}

\title{\textbf{Computational Linguistics} \\
Assignment 3\\
Context-free grammars and CKY parsing 
}
\author{Sangeet Sagar\\
            \texttt{sasa00001@stud.uni-saarland.de}
}


\date{\today}
% \pgfplotsset{compat=1.17}
\begin{document}

\maketitle
%#################################################################
\section{Introduction}
This assignment implements the CKY algorithm for bottom-up CFG parsing and applies it to the word and the parsing problem of English. Developed in 1960, the CKY algorithm is the most used chart parser for CFGs (context-free grammars) in CNF (Chomsky normal-form). It uses a dynamic programming algorithm to tell whether a string is in the language of grammar.

\section{Description}
The script has been integrated with multiple functionalities: 
\begin{itemize}
    \item For a given test sentence, check if it is in the language of CFG or not. Return \codeword{True} for the same.
    \item For a given test sentence compute all possible CYK parse trees and CYK chart
    \item For a given test sentence compute counts of all possible parse trees in two ways:
    \begin{itemize}
        \item Using back-pointer extract set of all parse trees and get their total count
        \item \textbf{Extra-credit} Just using back-pointer, maintain a \codeword{count} variable that increments itself recursively every time the back-pointer is called for a node. This generates all possible counts of CYK parsed trees without actually computing the parse trees.
    \end{itemize}
    \item Print a summary table for all test sentences and display if it's in the language of CFG and total counts of all possible trees computed in two ways discussed above.
    \item Print runtime.
    
\end{itemize}

\section{Requirements}
\begin{enumerate}
    \item Python: \codeword{3.8.3}
    \item NLTK: \codeword{3.5}
    \item Texttable: \codeword{1.6.3}. Install: \codeword{pip install texttable}
\end{enumerate}
\section{Project file structure}
\begin{Verbatim}
├── atis
│   ├── atis-grammar-cnf.cfg
│   ├── atis-grammar-original.cfg
│   ├── atis-test-sentences.txt
│   └── other_bad_sentences.txt
├── cky.py
├── README.md
└── results
    ├── summary_bad_sentences.txt
    ├── summary_tree_counts.txt
    ├── ten_sents_cyk_chart.txt
    └── ten_sents_parsed_trees.txt
 \end{Verbatim}

\section{Usage}
\begin{itemize}
    \item \textbf{Help}: for instructions on how to run the script with appropriate arguments.\\
        \codeword{python cky.py --help}\\
        \begin{lstlisting}
        python cky.py --help
        usage: cky.py [-h] 
                    [-show_chart SHOW_CHART] 
                    [-show_tree SHOW_TREE]
                    [-show_summary SHOW_SUMMARY]
                    grammar_f sents_f
        
        Cocke-Kasami-Younger (CKY) algorithm for bottom-up CFG parsing 
        Goals: 
            > Write CKY algorithm and use it as a recognizer of CFG. 
            > Extend it to a parser by adding back pointers 
            > Get counts of all possible CKY parse trees for each 
            sentence that is in the language of CFG 
        Functionalities: 
            > Create CKY chart
            > Create CKY parsed trees 
            > Get runtimes
        
        positional arguments:
          grammar_f                 path to grammar file
          sents_f                   path test sentences file
        
        optional arguments:
          -h, --help                show this help message and exit
          -show_chart SHOW_CHART    display CYK parsed chart
          -show_tree SHOW_TREE      display CYK parsed tree
          -show_summary SHOW_SUMMARY
        \end{lstlisting}


        \item \textbf{Run CYK parser}: Given CNF grammar and set of test sentences, check if these sentences are in the language of grammar and also display counts of all possible CKY parsed tress.\\
        \codeword{python cky.py atis/atis-grammar-cnf.cfg atis/atis-test-sentences.txt}
  
        \item Run and test the parser on some self-made sentences that are ungrammatical (i.e. not in the language of given CFG) \\
        \codeword{python cky.py atis/atis-grammar-cnf.cfg atis/other_bad_sentences.txt}
 
\end{itemize}
\section{Runtime}
\begin{itemize}
    \item \textbf{Total} runtime: 20.51 s
    \item \textbf{CYK parser} runtime: 17.76 s
    \item \textbf{Backpointer} runtime: 0.015 s
\end{itemize}
However, if you use optional arguments \codeword{-show_chart} or \codeword{-show_tree}, the total runtime is as follows:
\begin{itemize}
    \item Total runtime: \codeword{-show_chart}: 23.67 s
    \item Total runtime: \codeword{-show_tree}: 285.27 s
\end{itemize}

\section{Results Contents}
\begin{itemize}
    \item \texttt{summary\_tree\_counts.txt}: Summary table of given ATIS test set with 98 sentences. Display if the sentence is in the language of CFG and counts of all possible CYK parse trees.
    \item \texttt{ten\_sents\_parsed\_trees.txt}: Shows CYK parsed trees of the first 10 sentences from the ATIS test-set
    \item \texttt{ten\_sents\_cyk\_chart.txt}: Shows CYK chart of first 10 sentences from the ATIS test-set
    \item \texttt{summary\_bad\_sentences.txt}: (Summary table of some self-made sentences) Shows if the sentences are in the language of CFG and counts of the parse tree for each.
\end{itemize}

\section{Glimpse of results}
\begin{itemize}
    \item CKY tree of the sentence \codeword{show availability .}. \\
    A total of 3 trees are observed and they are:
\end{itemize}

\begin{Verbatim}
( 1 ) show availability .

Given sentence is in the language of CFG

              SIGMA
   ┌────────────┴───────────┐
   │                       JWB
   │            ┌───────────┴──────────┐
NOUN_NN      AVPNP_NN             pt_char_per
   │            │                      │
  show     availability                .

            SIGMA
  ┌───────────┴───────────┐
  │                      JXI
  │           ┌───────────┴──────────┐
NP_NN      NOUN_NN              pt_char_per
  │           │                      │
 show    availability                .

              SIGMA
   ┌────────────┴───────────┐
   │                       JKA
   │            ┌───────────┴──────────┐
VERB_VB       NP_NN               pt_char_per
   │            │                      │
  show     availability                .

\end{Verbatim}
\begin{itemize}
    \item Summary table for first 10 sentences.
\end{itemize}
\begin{Verbatim}
+-------+-------------------------------------+-------+------------+
| S.No. |       test sentence                 |  CFG  | parse tree |
|       |                                     |       |   counts   |
+=======+=====================================+=======+============+
| 1     | prices .                            | True  | 2          |
+-------+-------------------------------------+-------+------------+
| 2     | show availability .                 | True  | 3          |
+-------+-------------------------------------+-------+------------+
| 3     | show the flights .                  | True  | 2          |
+-------+-------------------------------------+-------+------------+
| 4     | milwaukee to detroit .              | True  | 2          |
+-------+-------------------------------------+-------+------------+
| 5     | indianapolis to seattle .           | True  | 2          |
+-------+-------------------------------------+-------+------------+
| 6     | list round trips .                  | True  | 11         |
+-------+-------------------------------------+-------+------------+
| 7     | list saturday flights .             | True  | 5          |
+-------+-------------------------------------+-------+------------+
| 8     | what aircraft is this .             | False | 0          |
+-------+-------------------------------------+-------+------------+
| 9     | list these economy fares .          | False | 0          |
+-------+-------------------------------------+-------+------------+
| 10    | list these city destinations .      | False | 0          |
+-------+-------------------------------------+-------+------------+
\end{Verbatim}
\bibliographystyle{plain}
\bibliography{references}
\end{document}
